\documentclass[a4paper,12pt]{article}
\usepackage{listings}
\lstset{language=Lisp}
\newcommand{\subpar}[1]{\medskip \noindent #1.}

\begin{document}

We're embedding the query evaluator inside the amb evaluator.  This
time, we don't explicitly define a driver loop.  Instead, we define
the procedures \lstinline!assert!! and \lstinline!query! in order to
interact with the query database.  The result of a query is displayed
one at a time and we need to type \lstinline!try-again! in order to
see the next solution if any.

Since the amb evaluator is searching for solutions in deep-first
order, we need to ``interleave'' the search results in the case of an
\lstinline!or! query.  Here we use, the \lstinline!ramb! operator
defined in \textbf{Exercise 4.50} instead of \lstinline!amb!.

The \lstinline!negate! operator's implementation also needs to be
pointed to.  Since we need to test if a query has no solution in order
to keep the frame otherwise we search for the next solution, we
introduce a new syntax
\begin{quote}
  \lstinline!if-fail-only <test> <result>!
\end{quote}

to the amb evaluator.  If the evaluation of \lstinline!<test>! fails, then we
return the evaluation of \lstinline!<result>!, otherwise we backtrack.
Here's the implementation

\begin{lstlisting}
(define (if-fail-only? exp)
  (tagged-list? exp 'if-fail-only))
(define if-fail-only-test cadr)
(define if-fail-only-result caddr)

(define (analyze-if-fail-only exp)
  (let ((test-proc (analyze (if-fail-only-test exp)))
        (res-proc (analyze (if-fail-only-result exp))))
    (lambda (env succeed fail)
      (test-proc env
                 (lambda (test fail2)
                   (fail))
                 (lambda ()
                   (res-proc env
                             (lambda (res fail2)
                               (succeed res fail2))
                             fail))))))
\end{lstlisting}

For the complete implementation of the query evaluator, see the file
\textbf{amb-query.scm}.

With our new implementation, if we enter an infinite loop, the
evaluator won't be stuck as in the implementation using a stream.
Instead, we will print the same result over and over again.  Consider
the following example:

\begin{lstlisting}
;;; Amb-Eval input:
(assert! '(married sarah michael))

;;; Starting a new problem 
Assertion added to data base
;;; Amb-Eval value:
ok

;;; Amb-Eval input:
(assert! '(rule (married ?x ?y)
                (married ?y ?x)))

;;; Starting a new problem 
Assertion added to data base
;;; Amb-Eval value:
ok

;;; Amb-Eval input:
(query '(married ?x ?y))

;;; Starting a new problem 
(married sarah michael)
;;; Amb-Eval value:
ok

;;; Amb-Eval input:
try-again
(married michael sarah)
;;; Amb-Eval value:
ok

;;; Amb-Eval input:
try-again
(married sarah michael)
;;; Amb-Eval value:
ok

;;; Amb-Eval input:
try-again
(married michael sarah)
;;; Amb-Eval value:
ok

;;; Amb-Eval input:
\end{lstlisting}

\end{document}
